worldmap

### 2021-06-04 analysis/visualization.Rmd
map by taxa

ggsave("study_map.jpeg")
```

@@

map_data("world") %>%
  ggplot(aes(long, lat, group = group)) +
  geom_polygon(fill = "white", colour = "grey") + 
  coord_map(xlim=c(-180,180), ylim=c(-57, 90)) +
  geom_point(data = study_data, aes(rarefyID_x, rarefyID_y, color = taxa), alpha = 0.5, inherit.aes = FALSE) +
  ggthemes::theme_map()
```

>>>>

#ggsave("study_map.jpeg")
```

@@

map_data("world") %>%
  ggplot(aes(long, lat, group = group)) +
  geom_polygon(fill = "white", colour = "grey") + 
  coord_map(xlim=c(-180,180), ylim=c(-57, 90)) +
  geom_point(data = study_data, aes(rarefyID_x, rarefyID_y, color = taxa), alpha = 0.5, inherit.aes = FALSE) +
  ggthemes::theme_map()

ggsave(here::here("figures/study_map.jpeg"))
```
